---
title: "Quiz01"
author: "Arora"
date: "September 26, 2017"
output: html_document
---

#I could not push this to github. I had it opened on my desktop but it would not let me push it. 

```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)

library(dplyr)
dt<-as.data.frame(d)
dt

```
###Quiz 2

#For some reason it is saying that curl is invalid, so I don't know if this is going to work; I'll update once this quiz is finished. 
#Also once again, it has disconnected from the project. The time that this quiz ended is: 3:55
```{r, eval=FALSE}
library(dplyr)
g<-data.frame(dt$first_name, dt$last_name, dt$gender, dt$height, dt$weight, dt$zombies_killed)
g

s<-subset(g, g$dt.gender == "Female")
s
  
s1<-mutate(s,s$dt.height>65 & s$dt.height<65)

s1<-if(d$height>65){
  label("over five foot five inches")
}
s1<-if(d$height<65){
  print("under five foot five inches")
}

library(ggplot2)
s1
p <- ggplot(data = s1, aes(x = height, y = zombies_killed))

#error because ggplot2 cannot make a graph with the data of class character 
``` 
#Quiz #3
pull in zombie data set
pull out all medical/nursing majors 
relationship between age and years of education
years as education as continuous variable
plot 
regression 95%
males are pink
females are blue

```{r}
library(curl)
f <- f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall17/zombies.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)

library(dplyr)
dt<-as.data.frame(d)
dt

g<-data.frame(dt, dt$gender, dt$years_of_education, dt$major, dt$age)
g

g<-subset(g, g$major == "medical/nursing")
g

```
```{r}
library(ggplot2)
p <- ggplot(data = g, aes(x = age, y = years_of_education), xlab("Age"), ylab("Years of Education")) +
  geom_point(aes(colour=factor(gender))) +
  geom_smooth(method ="lm", formula = y~x)
p
#this has not added color to the points correclty; if I add  female="blue", male="pink" this does not work 
```